Open Policing Project Tutorial

### 2019-03-05 nicar_tutorial.Rmd
Update data path

## NOTE(eric, justin): These next few lines will change a bit once we pin down 
## the ubs/data format situation.

## Load the data
# Replace the path below with the path to where your data lives
data_path <- "~/opp/data/states/pa/philadelphia/clean/philadelphia.rds"
stops <- read_rds(data_path)#$data

@@

stops %>% 
  group_by(subject_race) %>% 
  summarize(
    search_rate = mean(search_conducted),
    frisk_rate = mean(frisk_performed)
  )
```

@@

stops %>% 
  filter(search_conducted) %>% 
  group_by(subject_race) %>% 
  summarize(
    hit_rate = mean(contraband_found)
  )
```

@@

stops %>% 
  filter(search_conducted, district != "77") %>% 
  group_by(subject_race) %>% 
  summarize(
    hit_rate = mean(contraband_found)
  )
```

@@

~~
**NOTE FOR ERIC/JUSTIN/CHERYL/BETHANY:** I can add in another raw data intuition
section that's a basic raw data plot if you think the concept of the VOD test
is still confusing. But i want to keep things a bit briefer that way we have 
more time to field questions and have them actually type things in and think 
things through rather than just running code dan and i wrote...let me know what
you think though.
~~

@@

summary(mod1)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
#exp(summary(mod1)$coefficients["is_darkTRUE", "Estimate"])
```

@@

summary(mod2)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
# exp(summary(mod2)$coefficients["is_darkTRUE", "Estimate"])
```

>>>>

## Load the data
# Replace the path below with the path to where your data lives
# data_path <- "~/opp/data/states/pa/philadelphia/clean/philadelphia.rds"
# stops <- read_rds(data_path)$data
data_path <- "~/Desktop/pa_philadelphia_2019_02_25.rds"
stops <- read_rds(data_path)

@@

stops %>% 
  group_by(subject_race) %>% 
  summarize(
    search_rate = mean(search_conducted, na.rm = T),
    frisk_rate = mean(frisk_performed, na.rm = T)
  )
```

@@

stops %>% 
  filter(search_conducted) %>% 
  group_by(subject_race) %>% 
  summarize(
    hit_rate = mean(contraband_found, na.rm = T)
  )
```

@@

stops %>% 
  filter(search_conducted, district != "77") %>% 
  group_by(subject_race) %>% 
  summarize(
    hit_rate = mean(contraband_found, na.rm = T)
  )
```

@@

~~
**NOTE FOR ERIC/JUSTIN/CHERYL/BETHANY/HANS:** I can add in another raw data intuition
section that's a basic raw data plot if you think the concept of the VOD test
is still confusing. But i want to keep things a bit briefer that way we have 
more time to field questions and have them actually type things in and think 
things through rather than just running code dan and i wrote...let me know what
you think though.
~~

@@

summary(mod1)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
```

@@

summary(mod2)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
```
